---
title: "analysis"
author: "Devynn M Wulstein"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = FALSE)
```

```{r}
## Loading libraries
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
library(reshape2)
library(stringr) 
library(pROC)
library(ggpubr)

SmithsonVerkuilen2006=function(yi){
  n=length(yi)
  yo=(yi * (n-1) + 0.5) / n
  return(yo)
}
Inv.SmithsonVerkuilen2006=function(yo){
  n=length(yo)
  yi=(n*yo - 0.5)/(n-1)
  return(yi)
}


```

# Have you already run and saved the data from this file?

## Yes:
We have already run and manipulated the raw data. We can just start working on the IPM parameterizations. 
```{r LoadingEDITEDdata,}
load("data/Colony_Data_20210915_edited.rdata")
load("data/Colony_Data_20210915_edited_survival.rdata")

SiteNames     <- as.character(unique(ColonyLevel$Site))
GeneraNames   <- as.character(unique(ColonyLevel$Genus_Code))
IntervalYears <- unique(ColonyLevel$Interval)
No2015_int    <- IntervalYears[c(1,3,6,8,10,11,13)]
Yes2015_int <- IntervalYears[c(2,4,5,7,9,12)]
All_int <-IntervalYears

```

Skip down to 

## No:
We need to load in the raw transition level dataset, they need to be cleaned up slightly and manipulated into a format that can be used tp parameterize the IPMs.
### Loading dataframes and modifications
```{r RAWdata.}
# Loading dataframe(s)

#load updated dataframe
#load("data/Patch_And_Colony_Data_20210531.rdata")
load("data/Patch_And_Colony_Data_20210917.rdata")

#changing ln_ES/ln_SS from Na/-Inf to an actual value for recruitment/mortality
ColonyLevel$ln_SS <- log(ColonyLevel$StartingSize)
ColonyLevel$ln_ES <- log(ColonyLevel$EndingSize)

ColonyLevel$log10_SS <- log10(ColonyLevel$StartingSize)
ColonyLevel$log10_ES <- log10(ColonyLevel$EndingSize)
 
ColonyLevel$log10_SS <- as.numeric(ColonyLevel$log10_SS)
ColonyLevel$log10_SS[ColonyLevel$log10_SS == -Inf] <-NA

ColonyLevel <- cbind(ColonyLevel, data.frame(Survival = 
                                               1 - ColonyLevel$Mortality))

# Making the size term yearly
GY <- (ColonyLevel$ln_ES - ColonyLevel$ln_SS)*(1/ColonyLevel$Interval_Year)
ColonyLevel <- cbind(ColonyLevel, data.frame(ln_ESc = 
                                             ColonyLevel$ln_SS + GY))

GY <- (ColonyLevel$log10_ES - ColonyLevel$log10_SS)*(1/ColonyLevel$Interval_Year)
ColonyLevel <- cbind(ColonyLevel, data.frame(log10_ESc = 
                                             ColonyLevel$log10_SS + GY))
ColonyLevel$log10_ESc[ColonyLevel$log10_ESc == -Inf] <-NA

# Defining site IDs, genera names, and transition intervals (years) as lists
SiteNames <- as.character(unique(ColonyLevel$Site))
GeneraNames <- as.character(unique(ColonyLevel$Genus_Code))
IntervalYears <- unique(ColonyLevel$Interval)

# You need to change this to reflect the years where 2015 is not in the interval
# !! Stop here
# Want to do it nicer, but will figure that out later

#StYears=substr(IntervalYears,1,2)
#EndYears=substr(IntervalYears,4,5)
#Yes2015_int=which(StYears<=15&EndYears>15|StYears==15)
#No2015_int=which(EndYears<=15|StYears>15)
#No2015_int    <- IntervalYears[c(2,4,7,10,11,12)]
#Yes2015_int <- IntervalYears[c(1,3,5,6,8,9)]
All_int <-IntervalYears

#Changes death 0 and survival 1

surv_dat <- data.frame()
surv_dat_manual=ColonyLevel[,c("ColonyID","log10_SS","Survival","Genus_Code","Interval","SiteInterval","Site","N_t0","TransitionType","Interval_Years")]
surv_dat_manual=subset(surv_dat_manual,TransitionType!="RECR")
names(surv_dat_manual)=c("ColonyID","size","survival","Genus_Code","Interval","SiteInterval","Site","N_t0","TransitionType","Interval_Years")
surv_dat=surv_dat_manual
#names(surv_dat)

# #Now estimate annualized survival probabilites through binomial glm
# modS     <- glm(survival ~ size, family = "binomial" , data = surv_dat)
# modS_IY     <- glm(survival ~ size + log10(Interval_Years)+Genus_Code+Site+Interval, family = "binomial" , data = surv_dat)
# modS_IY2     <- glm(survival ~ (size + log10(Interval_Years)+Genus_Code+Site+Interval)^2, family = "binomial" , data = surv_dat)
# smodS <- summary(modS)
# smodS_IY <- summary(modS_IY)
# smodS_IY <- summary(modS_IY2)
# 
# confint(modS_IY)
# 
# #given Interval_Years fit re-predict survivorship probability to annual period (i.e. interval==1)
# #We'll use "ann_survival" for the rest of the model fitting below?? TAO 2021-09-13
# surv_dat_ann=surv_dat
# surv_dat_ann$Interval_Years=1
# surv_dat$ann_survival=predict(modS_IY2,newdata = surv_dat_ann,type="response")
# 
# #Check the fits (for fun)
# modS_ann     <- glm(ann_survival ~ size, family = "binomial" , data = surv_dat)
# smodS_ann <- summary(modS_ann)
# 
# 
# annsp=ggplot(surv_dat,aes(x=size))+
#   geom_point(aes(y=survival,color=Interval_Years))+
#   stat_smooth(aes(y=survival),method="loess",color="grey",se=F)+
#   geom_point(aes(y=ann_survival),color="blue")+
#   stat_smooth(aes(y=ann_survival),method="loess",color="blue",se=F)+
#   scale_color_viridis_c()+
#   facet_grid(Site~Genus_Code)+ylim(c(0,1))
# ggsave(filename = "annsp_overfitinteraction.jpg",plot = annsp,height=12,width=9)


# sizecheck=left_join(x = surv_dat_manual[,c("ColonyID","Genus_Code","Site","Interval","survival","size")],
#                     y = surv_dat[,c("ColonyID","Genus_Code","Site","Interval","survival","size")],
#                     by=c("ColonyID","Genus_Code","Site","Interval","survival"))
# dim(sizecheck)
# 
# scp=ggplot(sizecheck,aes(size.x,size.y))+geom_point()+facet_grid("survival")
# length(which(sizecheck$size.x!=sizecheck$size.y))
# 
# dim(sizecheck)
# 
# sdp=ggplot(surv_dat,aes(size,survival))+geom_point()+stat_smooth(method="loess")+facet_grid("Genus_Code")
# sdp_m=ggplot(surv_dat_manual,aes(size,survival))+geom_point()+stat_smooth(method="loess")+facet_grid("Genus_Code")
# sdp+sdp_m


# Change these file names when saving data to refect the new changes
save(ColonyLevel, file="data/Colony_Data_20210915_edited.rdata")
save(surv_dat, file="data/Colony_Data_20210915_edited_survival.rdata")
```


# Where we run the models
## Full growth and survival models
The two chunks below will fit the growth and survival data for the full set of site and year interval combinations as well as the full model. The outputs are .rdata files that have (1) the site/interval combinations alone, (2) the combined dataframes with the regional model, and (3) the combined data with the NAs removed so that it is easier to manipulate in the IPM one.

Make sure to change the name of the file so that you do not over write an old file if that is something you care about!! 
```{r Genera + Site + Years Mod Growth,}
 GrowthDataFrame <- data.frame()

################################################################################
######### Genera + Site + Interval Years  models ###############################
########## GROWTH ! ############################################################
################################################################################
# define the parms for model loop

Focus          <- GeneraNames
subFocus       <- SiteNames
subFocus2      <- IntervalYears
altsFocus2     <- All_int
LoopLength     <- length(Focus)
LoopLengthSF   <- length(subFocus)
LoopLengthSF2  <- length(subFocus2)
LoopLengthaSF2 <- length(altsFocus2)

# Change this value to change the # of minimum data points at each site interval. If it is below this value then the model will not run and will skip this site/interval combination
minTrans <- 20 

# Change these parameters to change which intervals we are using
Ints <- altsFocus2
Leng <- LoopLengthaSF2

# Change the file name that the data is being saved as
# Just change it here, this should be the main name (it will be modified below too, but not by you)
Name <- "SiteInterval_All_20210915"

for (i in 1:LoopLength){
  
  # subset Genus_Code for specific genera
  subset1 <- subset(ColonyLevel, Genus_Code == Focus[i])

  for (v in 1:LoopLengthSF){
    
    # redefine the matrix for each Focus step
    growth <- matrix(0, nrow = 2, ncol = Leng)
    note   <- Var <- aic <- R2 <- c()
    
    # subsetting for growth & shrinkage
    subset2 <- subset(subset1, TransitionTypeSimple == "GROWTH" | 
                 TransitionTypeSimple == "SHRINK")
    
    # subsetting growth & shrinkage for specific Site
    subset3 <- subset(subset2, Site == subFocus[v])
    
    for (y in 1:Leng){
      
      #subsetting genera specific & Site specific into interval year specific
      subset4 <- subset(subset3, Interval == Ints[y])
      
      log10_SS  <- subset4$log10_SS
      log10_ESc <- subset4$log10_ESc
      
      if (length(log10_SS) > minTrans){
        mod        <- lm(log10_ESc ~ log10_SS)
        note[y]    <- length(log10_SS)
        growth[,y] <- coef(mod)
        Var[y]     <- (summary(mod)$sigma)^2
        R2[y]      <- summary(mod)$adj.r.squared
        aic[y]     <- AIC(mod)}
      
      if (length(log10_SS) <= minTrans){
        #setting values to NaNs
        note[y] <- length(log10_SS)
        growth[,y] <- NA
        Var[y]     <- NA
        R2[y]      <- NA
        aic[y]     <- NA}

      df <- data.frame(Sites = subFocus[v], Years = Ints[y], 
                       Genus_Code = Focus[i], g.int = growth[1,y], 
                       g.slp = growth[2,y], g.var = Var[y], AIC = aic[y], 
                       R.sqd = R2[y], GModel.n = note[y])
      
      GrowthDataFrame <- rbind(GrowthDataFrame,df)
}}}

for (f in 1:length(Focus)){
  
  subset1 <- subset(ColonyLevel, Genus_Code == Focus[f])
  subset2 <- subset(subset1, TransitionTypeSimple == "GROWTH" | 
                 TransitionTypeSimple == "SHRINK")
  subset3 <- subset(subset2, Interval %in% Ints)
  
  mod <- lm(log10_ESc ~ log10_SS, subset3)
  note    <- length(subset2$log10_SS)
  growth <- coef(mod)
  Var     <- (summary(mod)$sigma)**2
  R2      <- summary(mod)$adj.r.squared
  aic     <- AIC(mod)
  
  df <- data.frame(Sites = "All Sites", Years = "All Years", Genus_Code = Focus[f],
                   g.int = growth[1], g.slp = growth[2], 
                   g.var = Var, AIC = aic, R.sqd = R2, 
                   GModel.n = note)
        
  GrowthDataFrame <- rbind(GrowthDataFrame,df)
}


save(GrowthDataFrame, file = sprintf("data/%s_Gmodfits.rdata",Name))
```


```{r Genera + Site + Years Mod Survival,}

SurvivalDataFrame <- data.frame()
################################################################################
######### Genera + Site + Interval Years  models ###############################
## SURVIVAL ! ##################################################################
################################################################################
# define the parms for model loop
# Now with a second "Focus"

Focus          <- GeneraNames
subFocus       <- SiteNames
subFocus2      <- IntervalYears
altsFocus2     <- All_int
LoopLength     <- length(Focus)
LoopLengthSF   <- length(subFocus)
LoopLengthSF2  <- length(subFocus2)
LoopLengthaSF2 <- length(altsFocus2)

# Change this value to change the # of minimum data points at each site interval. If it is below this value then the model will not run and will skip this site/interval combination
minTrans <- 20

# Change these parameters to change which intervals we are using
Ints <- altsFocus2
Leng <- LoopLengthaSF2

# Change the file name that the data is being saved as
# Just change it here, this should be the main name (it will be modified below too, but not by you)

Name <- "SiteInterval_All_20210915"

for (i in 1:LoopLength){
  
  # subset Genus_Code for specific genera
  subset1_S <- subset(surv_dat, Genus_Code == Focus[i])

  for (v in 1:LoopLengthSF){
    
    # redefine the matrix for each Focus step
    survival <- matrix(0, nrow = 2, ncol = Leng)
    Snote <- aic_S <- pR2 <- c()
    
    #subsetting genera specific into Site specific
    subset2_S <- subset(subset1_S, Site == subFocus[v])
    
    for (y in 1:Leng){
      #subsetting genera specific & Site specific into interval year specific
      subset3_S <- subset(subset2_S, Interval == Ints[y])

# Survival model 
    if (length(subset3_S$size) >= minTrans){
      #this is where we fit the annualized probability of survival (see surv_dat section above)
      modS     <- glm(survival ~ size, family = "binomial" , data = subset3_S) 
      #modS     <- glm(ann_survival ~ size, family = "binomial" , data = subset3_S) 
      smodS <- summary(modS)
      nullmodS <- glm(survival ~ 1, family = "binomial", data = subset3_S)
      #nullmodS <- glm(ann_survival ~ 1, family = "binomial", data = subset3_S)
      pR2[y]   <- 1-(smodS$deviance/smodS$null.deviance)#1 - logLik(modS) / logLik(nullmodS)
      Snote[y] <-  length(subset3_S$size)
      
      survival[,y] <- coef(modS)
      aic_S[y]     <- AIC(modS)
      
      }
    
    if (length(subset3_S$size) < minTrans){
      #setting values to NaNs
      Snote[y]     <- length(subset3_S$size)
      survival[,y] <- NA
      aic_S[y]     <- NA
      pR2[y]       <- NA
      }
    
  
    # Row binding the model results into the survival model dataframe
    
    dfS <- data.frame(Sites = subFocus[v], Years = Ints[y], Genus_Code = Focus[i],
                                  s.int = survival[1,y], s.slp = survival[2,y], 
                                  AIC = aic_S[y], pR2=pR2[y],
                                  SModel.n = Snote[y]) 
    
    SurvivalDataFrame <- rbind(SurvivalDataFrame,dfS)
      
    }}}

for (i in 1:length(Focus)){
  subset1_S <- subset(surv_dat, Genus_Code == Focus[i])
  subset2_S <- subset(subset1_S, Interval %in% Ints)
  
  if(length(unique(subset2_S))>1){print("FLAG!!!!, subset2_S has more than one Interval_Year")}
  
  modS      <- glm(survival ~ size, family = "binomial" , data = subset2_S)
  smodS     <- summary(modS)
  nullmodS  <- glm(survival ~ 1, family = "binomial", data = subset2_S)
  pR2       <- 1-(smodS$deviance/smodS$null.deviance)#1 - logLik(modS) / logLik(nullmodS)#
  Snote     <-  length(subset1_S$size)
  
  survival <- coef(modS)
  aic_S    <- AIC(modS)
  dfS      <- data.frame(Sites = "All Sites", Years = "All Years", 
                         Genus_Code = Focus[i], s.int = survival[1], 
                         s.slp = survival[2], AIC = aic_S, pR2=pR2, 
                         SModel.n = Snote) 
      
  SurvivalDataFrame <- rbind(SurvivalDataFrame,dfS)
}

save(SurvivalDataFrame, file = sprintf("data/%s_Smodfits.rdata", Name))

combo <- cbind(GrowthDataFrame,SurvivalDataFrame[4:8])
save(combo, file = sprintf("data/%s_allmodfits.rdata",Name))

no_NAs <- na.omit(combo)
data <- no_NAs[order(no_NAs$Sites),]
save(data, file = sprintf("data/%s_allmodfits_noNAs.rdata",Name))

```

# Do you care about the interactions? 
## Yes? Then continue on!
## No? Then move to IPM analysis Markdown! 
#### Notes for Caroline & Devynn with understanding interactions (and R's models in general).

The interaction models return the differences from intercept & slope for each interaction. You have to calculate the differences when you have run the model to get the actual values for slope and intercept. That is what the following functions do, they were edited from material given to me by Mike McWilliam.

```{r Interactions,}
###### Interactions code from Mike #############################################
## Functions to calculate the slope and intercepts from interactions ###########

interceptz <-function(mod, u_predict){ 
	int <- rep(coef(mod)[[1]], length(u_predict))
	for (i in 2:length(u_predict)) {
	  Name <- grepl(u_predict[i], 
	                names(coef(mod))) & !grepl(names(coef(mod))[2], 
	                                           names(coef(mod)))
	  if (sum(Name) == 0) int[i] <- NA
	  else {
	  int[i] <- int[i] + coef(mod)[Name]}}
	int} 
	
slopez <-function(mod, u_predict){ 
	slp <- rep(coef(mod)[[2]], length(u_predict))
	for (i in 2:length(u_predict)) { 
	  Name <- grepl(u_predict[i],
	                names(coef(mod))) & grepl(names(coef(mod))[2],
	                                          names(coef(mod)))
	  if (sum(Name) == 0) slp[i] <- NA
	  else {
	  slp[i] <- slp[i] + coef(mod)[Name]}}
	slp}


```

```{r}
################################################################################
# Model interactions by genus: Growth ##########################################
################################################################################
################################################################################

Growth <- subset(ColonyLevel, TransitionTypeSimple == "GROWTH" | 
                   TransitionTypeSimple == "SHRINK")

# Only run this initially
# we will compare this to other models calculated separately 
dt               <- data.frame() # defining the full data frame
df_SiteYear_coef <- data.frame()
df_Year_coef     <- data.frame()
df_Site_coef     <- data.frame()
df_coef          <- data.frame()

# Separating the growth data frame by genera #
POCS <- Growth[Growth$Genus_Code==GeneraNames[1],]
POSP <- Growth[Growth$Genus_Code==GeneraNames[2],]
MOSP <- Growth[Growth$Genus_Code==GeneraNames[3],]
```

#Growth
```{r}
Choice <- POSP # Change this to the Genera Name above that you care about

x2_S   <- sort(unique(Choice$Site)) # your second predictor
x2_Y   <- sort(unique(Choice$Interval)) # another predictor for time
x2_SY  <- sort(unique(Choice$SiteInterval)) # another predictor where time & site are together 

mod           <- lm(ln_ESc ~ ln_SS, data = Choice)
mod_frag       <- lm(ln_ESc ~ ln_SS+N_t0, data = Choice)

mod_site      <- lm(ln_ESc ~ ln_SS + Site + Site*ln_SS, data = Choice)
mod_year      <- lm(ln_ESc ~ ln_SS + Interval + Interval*ln_SS, data = Choice)
mod_site_year <- lm(ln_ESc ~ ln_SS + 
                      SiteInterval + SiteInterval*ln_SS, data = Choice)

dt <- rbind(dt, data.frame(Sites=rep('All_Sites',length = 1),
                           Years=rep('All_Years',length = 1),
                           Genus_Code=rep(Choice$Genus_Code[1],1),
                           g.int=coef(mod)[1],
                           g.slp=coef(mod)[2]))
                           #g.var=(summary(mod)$sigma)**2))

dt <- rbind(dt, data.frame(Sites=x2_S,Years=rep('All_Years',length(x2_S)),
                           Genus_Code=rep(Choice$Genus_Code[1],length(x2_S)),
                           g.int=interceptz(mod_site, x2_S),
                           g.slp=slopez(mod_site, x2_S)))

dt <- rbind(dt, data.frame(Years=x2_Y,Sites=rep('All_Sites',length(x2_Y)),
                           Genus_Code=rep(Choice$Genus_Code[1], length(x2_Y)),
                           g.int=interceptz(mod_year, x2_Y),
                           g.slp=slopez(mod_year, x2_Y)))

dt <- rbind(dt, data.frame(Sites=x2_SY, Years=x2_SY,  
                           Genus_Code=rep(Choice$Genus_Code[1], length(x2_SY)),
                           g.int=interceptz(mod_site_year, x2_SY),
                           g.slp=slopez(mod_site_year, x2_SY)))


# Saving parameters & model summaries into dataframes
df               <- as.data.frame(coef(summary(mod)))
df               <- cbind(df, data.frame(Genus_Code = rep(Choice$Genus_Code[1],
                                     dim(df["Estimate"])[1])))
df_coef          <- rbind(df_coef, df)

df               <- as.data.frame(coef(summary(mod_site)))
df               <- cbind(df, data.frame(Genus_Code = rep(Choice$Genus_Code[1],
                                     dim(df["Estimate"])[1])))
df_Site_coef     <- rbind(df_Site_coef, df)


df               <- as.data.frame(coef(summary(mod_year)))
df               <- cbind(df, data.frame(Genus_Code = rep(Choice$Genus_Code[1],
                                     dim(df["Estimate"])[1])))
df_Year_coef     <- rbind(df_Year_coef, df)


df               <- as.data.frame(coef(summary(mod_site_year)))
df               <- cbind(df, data.frame(Genus_Code = rep(Choice$Genus_Code[1],
                                     dim(df["Estimate"])[1])))
df_SiteYear_coef <- rbind(df_SiteYear_coef, df)


#Compare model fits
AIC(mod)
AIC(mod_site)
AIC(mod_year)
AIC(mod_site_year)
anova(mod, mod_site)
anova(mod,mod_year)
anova(mod, mod_site_year)
anova(mod_year,mod_site_year)

#model assumptions
#Residuals should have constant variance and no trend in mean (residuals vs fitted plot plot line should be linear)
#Residuals should be Gaussian (Q-Q plot residuals should fall on 1:1 line)
#Constant error variance (Scale-Location plot)

fitvalues <- fitted(mod_year) #fitted values
residu <- residuals(mod_year) #residuals
standresid <- rstandard(mod_year) #standardized residuals
shapiro.test(residu) #data should be normal(p>0.05)
cor.test(fitvalues, sqrt(abs(standresid)), method = "k" ) #want there to be no correlation (p>0.05) and tau to be a small number (weak association)


#plot model residuals
par(mfrow=c(2,2))
plot(mod_year) #change for each model

```

```{r}
# Run this after running the chunk above for each genera

save(dt, file = "data/Growth_intmod_params.rdata")
save(df_coef, file = "data/Growth_mod_summary.rdata")
save(df_Site_coef, file = "data/Growth_intmod_summary_site.rdata")
save(df_Year_coef, file = "data/Growth_intmod_summary_year.rdata")
save(df_SiteYear_coef, file = "data/Growth_intmod_summary_site_year.rdata")

summarys <- load("data/Growth_intmod_summary_site_year.rdata")
```

```{r,}
################################################################################
# Model interactions by genus: Survival ########################################
################################################################################
# subsetting the survival data frame by genera 
POCS <- surv_dat[surv_dat$Genus_Code==GeneraNames[1],]
POSP <- surv_dat[surv_dat$Genus_Code==GeneraNames[2],]
MOSP <- surv_dat[surv_dat$Genus_Code==GeneraNames[3],]

# Initializing data frames to save model slopes and summaries
# Only run at beginning
dS               <- data.frame()
df_SiteYear_coef <- data.frame()
df_Year_coef     <- data.frame()
df_Site_coef     <- data.frame()
df_coef          <- data.frame()
```

```{r RunSurvivalIntz,}

# Change this each time for the different Genus Codes
# This just makes it into a generic name to change once in beginning & not have to change multiple times in the code
Choice <- POSP

x2_S   <- sort(unique(Choice$Site)) # your second predictor
x2_Y   <- sort(unique(Choice$Interval)) # another predictor for time
x2_SY  <- sort(unique(Choice$SiteInterval)) # another predictor where time & site are together 

nullmodS <- glm(survival ~ 1, family = "binomial", data = Choice)
modS           <- glm(survival ~ size, family = "binomial", data = Choice) #subset by site and interval and run the mod to get the g.var
modS_frag           <- glm(survival ~ size+N_t0, family = "binomial", data = Choice) #subset by site and interval and run the mod to get the g.var
1- (logLik(modS) / logLik(nullmodS))
1- (logLik(modS_frag) / logLik(nullmodS))


s.modS=summary(modS)
s.modS_frag=summary(modS_frag)
pr2=1-(s.modS$deviance/s.modS$null.deviance)
pr2=1-(s.modS_frag$deviance/s.modS_frag$null.deviance)
modS_site      <- glm(survival ~ size + Site + Site*size, 
                      family = "binomial", data = Choice)
modS_year      <- glm(survival ~ size + Interval + 
                        Interval*size, family = "binomial", data = Choice)
modS_site_year <- glm(survival ~ size + SiteInterval + 
                        SiteInterval*size, family = "binomial", data = Choice)

# Saving parameters & model summaries into dataframes
dS <- rbind(dS, data.frame(Sites=rep('All_Sites',1),Years=rep('All_Years',1),
                           Genus_Code=rep(Choice$Genus_Code[1],1),
                           s.int=coef(modS)[1],
                           s.slp=coef(modS)[2]))

dS <- rbind(dS, data.frame(Sites=x2_S,Years=rep('All_Years',length(x2_S)),
                           Genus_Code=rep(Choice$Genus_Code[1],length(x2_S)),
                           s.int=interceptz(modS_site, x2_S),
                           s.slp=slopez(modS_site, x2_S)))

dS <- rbind(dS, data.frame(Years=x2_Y,Sites=rep('All_Sites',length(x2_Y)), 
                           Genus_Code=rep(Choice$Genus_Code[1], length(x2_Y)),
                           s.int=interceptz(modS_year, x2_Y),
                           s.slp=slopez(modS_year, x2_Y)))

dS <- rbind(dS, data.frame(Sites=x2_SY, Years=x2_SY,  
                           Genus_Code=rep(Choice$Genus_Code[1], length(x2_SY)),
                           s.int=interceptz(modS_site_year, x2_SY),
                           s.slp=slopez(modS_site_year, x2_SY)))

df               <- as.data.frame(coef(summary(modS)))
df               <- cbind(df, data.frame(Genus_Code = rep(Choice$Genus_Code[1],
                                     dim(df["Estimate"])[1])))
df_coef          <- rbind(df_coef, df)

df               <- as.data.frame(coef(summary(modS_site)))
df               <- cbind(df, data.frame(Genus_Code = rep(Choice$Genus_Code[1],
                                     dim(df["Estimate"])[1])))
df_Site_coef     <- rbind(df_Site_coef, df)


df               <- as.data.frame(coef(summary(modS_year)))
df               <- cbind(df, data.frame(Genus_Code = rep(Choice$Genus_Code[1],
                                     dim(df["Estimate"])[1])))
df_Year_coef     <- rbind(df_Year_coef, df)


df               <- as.data.frame(coef(summary(modS_site_year)))
df               <- cbind(df, data.frame(Genus_Code = rep(Choice$Genus_Code[1],
                                     dim(df["Estimate"])[1])))
df_SiteYear_coef <- rbind(df_SiteYear_coef, df)

#Compare survival model fits
survivalAICs <- AIC(modS,modS_site,modS_year,modS_site_year)
survivalAICs

anova(modS, modS_site)
anova(modS,modS_year)
anova(modS, modS_site_year)
anova(modS_year,modS_site_year)


#Calculate McFadden's Pseudo R2
nullmodS <- glm(survival ~ 1, family = "binomial", data = Choice)
1- logLik(modS) / logLik(nullmodS)
nullmodS_site <- glm(survival ~ 1, family = "binomial", data = Choice)
1- logLik(modS_site) / logLik(nullmodS_site)
nullmodS_year <- glm(survival ~ 1, family = "binomial", data = Choice)
1- logLik(modS_year) / logLik(nullmodS_year)
nullmodS_site_year <- glm(survival ~ 1, family = "binomial", data = Choice)
1- logLik(modS_site_year) / logLik(nullmodS_site_year)



#plot model residuals
# png(filename = "figs/survivalresiduals.png")
 par(mfrow=c(2,2))
 plot(mod) #change for each model
# dev.off()

```

```{r SaveSurvival,}
# Run this after running the chunk above for each genera

save(dS, file = "data/Survival_intmod_params.rdata")
save(df_coef, file = "data/Survival_mod_summary.rdata")
save(df_Site_coef, file = "data/Survival_intmod_summary_site.rdata")
save(df_Year_coef, file = "data/Survival_intmod_summary_year.rdata")
save(df_SiteYear_coef, file = "data/Survival_intmod_summary_site_year.rdata")
```

### Reproduction
```{r RecGenSubset, eval=TRUE}
# Run at the beginning of calculating recruitment stuff
# Sepearting by genera
POCS <- ColonyLevel[ColonyLevel$Genus_Code==GeneraNames[1],]
POSP <- ColonyLevel[ColonyLevel$Genus_Code==GeneraNames[2],]
MOSP <- ColonyLevel[ColonyLevel$Genus_Code==GeneraNames[3],]

dr      <- data.frame()
dr_size <- data.frame()
```

```{r SizeINDRecs,}
# Rerun for all of the genera 
Choice <- POCS

Tc   <- 0.6 # time cut off for sampling period obviously change value to reflect reality
Cutz <- which(Choice$Interval_Years < Tc) # returns index for sampling periods less than Tc

# Converting too small sampling periods into NAs to eliminate additional zeros
Choice$Recruit[Cutz] <- NA

# We care about Intervals, Sites, & SiteIntervals
Ints      <- unique(Choice$Interval)
Sites     <- unique(Choice$Site)
SiteInts  <- unique(Choice$SiteInterval)
recs_I    <- c()
recs_S    <- c()
recs_SI   <- c()


for (i in 1:length(Ints)){
  times     <- c()
  a_recs    <- Choice$Recruit[which(Choice$Interval == Ints[i])]
  times     <- round(Choice$Interval_Years[which(Choice$Interval ==
                                                   Ints[i])])
  recs_I[i] <- round(sum(a_recs/times),2)
}

for (i in 1:length(Sites)){
  times <- c()
  a_recs  <- Choice$Recruit[which(Choice$Site == Sites[i])]
  times   <- round(Choice$Interval_Years[which(Choice$Site == Sites[i])])
  recs_S[i] <- round(sum(a_recs/times),2)
}

for (i in 1:length(SiteInts)){
  times      <- c()
  a_recs     <- Choice$Recruit[which(Choice$SiteInterval == SiteInts[i])]
  times      <- round(Choice$Interval_Years[which(Choice$SiteInterval == 
                                                 SiteInts[i])])
  recs_SI[i] <- round(sum(a_recs/times),2)
}



sites <- rep('All_Sites',length(recs_I)) #combine all the sites
ts    <- Ints

dr <- rbind(dr,data.frame(Genus_Code=rep(Choice$Genus_Code[1],length(recs_I)),
                  Tots_recs_peryear=recs_I,
                  Sites=sites,
                  Years=ts))

sites <-  Sites
ts    <- rep('All_Years',length(recs_S)) #combine all intervals

dr <- rbind(dr,data.frame(Genus_Code=rep(Choice$Genus_Code[1],length(recs_S)),
                  Tots_recs_peryear=recs_S,
                  Sites=sites,
                  Years=ts))

sites <-  SiteInts
ts    <- SiteInts

dr <- rbind(dr,data.frame(Genus_Code=rep(Choice$Genus_Code[1],length(recs_SI)),
                  Tots_recs_peryear=recs_SI,
                  Sites=sites,
                  Years=ts))

```

```{r SizedepRecs,}
# Rerun for all of the genera 
Choice <- POCS

Tc   <- 0.6 # time cut off for sampling period obviously change value to reflect reality
Cutz <- which(Choice$Interval_Years < Tc) # returns index for sampling periods less than Tc

Data_Min <- 30

# Converting too small sampling periods into NAs to eliminate additional zeros
Choice$Recruit[Cutz] <- NA

# We care about Intervals, Sites, & SiteIntervals
Ints      <- unique(Choice$Interval)
Sites     <- unique(Choice$Site)
SiteInts  <- unique(Choice$SiteInterval)
recs_I    <- c()
recs_S    <- c()
recs_SI   <- c()


for (i in 1:length(Ints)){ #if the time interval doesn't have enough data points, give it an NA
  
  if (length(Choice$Interval == Ints[i]) <= Data_Min){
    recs_I[i] <- NA
  }
  else {
    times     <- c()
    areas     <- c()
    a_recs    <- Choice$Recruit[which(Choice$Interval == Ints[i])] #numb of recruits per time interval
    times     <- round(Choice$Interval_Years[which(Choice$Interval == Ints[i])]) #each time interval (but rounded)
    areas     <- sum(Choice$StartingSize[which(Choice$Interval == Ints[i])]) #sum of area of "parent corals"
    #a_recs   <- a_recs/areas #calc numb recruits per area
    recs_I[i] <- sum(a_recs/times)/areas #recruits per year per cm of adults rounded to 2 decimal places
    
  }
  
  }

for (i in 1:length(Sites)){
  times   <- c()
  areas   <- c()
  a_recs  <- Choice$Recruit[which(Choice$Site == Sites[i])]
  times   <- round(Choice$Interval_Years[which(Choice$Site == Sites[i])])
  areas   <- round(Choice$StartingSize[which(Choice$Site == Sites[i])])
  recs_S[i] <- round(sum(a_recs/areas * times),2)
}

for (i in 1:length(SiteInts)){
  times   <- c()
  areas   <- c()
  a_recs  <- Choice$Recruit[which(Choice$SiteInterval == SiteInts[i])]
  areas   <- Choice$Interval_Years[which(Choice$SiteInterval == 
                                                 SiteInts[i])]
  times   <- round(Choice$Interval_Years[which(Choice$SiteInterval == 
                                                 SiteInts[i])])
  areas   <- round(Choice$StartingSize[which(Choice$SiteInterval == 
                                                 SiteInts[i])])
  recs_SI[i] <- round(sum(a_recs/areas * times),2)
}



sites <- rep('All_Sites',length(recs_I)) 
ts <- Ints

dr_size <- rbind(dr_size,
                 data.frame(Genus_Code=rep(Choice$Genus_Code[1],length(recs_I)),
                 Tots_recs_peryear=recs_I,
                 Sites=sites,
                  Years=ts))

sites <-  Sites
ts <- rep('All_Years',length(recs_S))

dr_size <- rbind(dr_size,
                 data.frame(Genus_Code=rep(Choice$Genus_Code[1],length(recs_S)),
                 Tots_recs_peryear=recs_S,
                 Sites=sites,
                  Years=ts))

sites <-  SiteInts
ts <- SiteInts

dr_size <- rbind(dr_size,
                 data.frame(Genus_Code=rep(Choice$Genus_Code[1],length(recs_SI)),
                 Tots_recs_peryear=recs_SI,
                 Sites=sites,
                  Years=ts))

```

```{r SaveRecData,}
save(dr, file = "data/Recruitment_sizeIndependent.rdata")
save(dr_size, file = "data/Recruitment_sizeDependent.rdata")

```

Putting the data into a dataframe that will work best for the matrix visualization stuff
```{r loadingDFs,}
# Loading in the data from above (this chunk can be run without running the stuff above!!)
GrowthModel   <- load("data/Growth_intmod_params.rdata")
SurvivalModel <- load("data/Survival_intmod_params.rdata")
Recruit_indep <- load("data/Recruitment_sizeIndependent.rdata")
Recruit_dep  <- load("data/Recruitment_sizeDependent.rdata")


POCS_G <- dt[dt$Genus_Code == GeneraNames[1],]
POSP_G <- dt[dt$Genus_Code == GeneraNames[2],]
MOSP_G <- dt[dt$Genus_Code == GeneraNames[3],]

POCS_S <- dS[dS$Genus_Code == GeneraNames[1],]
POSP_S <- dS[dS$Genus_Code == GeneraNames[2],]
MOSP_S <- dS[dS$Genus_Code == GeneraNames[3],]

POCS_R <- dr[dr$Genus_Code == GeneraNames[1],]
POSP_R <- dr[dr$Genus_Code == GeneraNames[2],]
MOSP_R <- dr[dr$Genus_Code == GeneraNames[3],]

POCS_Rdep <- dr_size[dr_size$Genus_Code == GeneraNames[1],]
POSP_Rdep <- dr_size[dr_size$Genus_Code == GeneraNames[2],]
MOSP_Rdep <- dr_size[dr_size$Genus_Code == GeneraNames[3],]

```

```{r fixingDFs,}
#split the site interval and flip the sites/intervals
Change <- POSP_R #change this variable rather than having to change it everywhere
these  <- grepl('\n',Change$Sites)
Change[these,] <- separate(Change[these,], col=Sites, 
                          into = c("Sites","Years"), sep = "\n" )

POSP_R <- Change #change this variable rather than having to change it everywhere

```

```{r PlotGrowthMatrix,}
#Growth
GPlotz <- POSP_G #change this variable

plotz<- ggplot(GPlotz, aes(x=Sites, y=Years)) + 
  geom_raster(aes(fill = g.slp))+ #change fill to look at diff VR functions
  scale_fill_gradient2(low = "blue", high = "red", mid="white",midpoint = GPlotz$g.int[1],na.value = "gray" )+
  labs(title = sprintf("Growth matrix visualization: %s", GPlotz$Genus_Code[1])) + theme_gray() +
  theme(plot.title = element_text(size = 20, face = "bold"), axis.text.x =  element_text(angle = 45, hjust = 1)) 
ggsave(filename = sprintf("Figures/%s_growthmatrix_%s.png",
                  GPlotz$Genus_Code[1],"int"), plot = plotz)

```

```{r PlotSurv_Matrix,}
#################
#Survival

SPlotz <- POSP_S #change this variable
plotz <- ggplot(SPlotz, aes(x=Sites, y=Years)) + 
  geom_raster(aes(fill = s.int))+ #change fill to look at diff VR functions
  scale_fill_gradient2(low = "blue", high = "red", mid="white",midpoint = SPlotz$s.int[1],na.value = "grey" )+
  labs(title = sprintf("Survival matrix visualization: %s", SPlotz$Genus_Code[1])) + theme_dark() +
  theme(plot.title = element_text(size = 20, face = "bold"), axis.text.x =  element_text(angle = 45, hjust = 1)) 
ggsave(filename = sprintf("Figures/%s_survivalmatrix_%s.png",
                  SPlotz$Genus_Code[1],"int"), plot = plotz)

```

```{r PlotRecruitMatrix,}
#need to print # of transitions on recruitment matrix
table(ColonyLevel$Site)

#Recruitment

#log transformed Recruitment
RPlotz <- POSP_R #change this variable

plotz <- ggplot(RPlotz, aes(x=Sites, y=Years)) + 
  geom_raster(aes(fill = log10(Tots_recs_peryear) ))+ #change fill to look at diff VR functions
  scale_fill_gradient(low = "grey90", high = "purple" )+
  labs(title = sprintf("Recruitment matrix visualization: %s", RPlotz$Genus_Code[1])) + theme_bw() +
  theme(plot.title = element_text(size = 20, face = "bold"), axis.text.x =  element_text(angle = 45, hjust = 1)) 
ggsave(filename = sprintf("Figures/%s_indeprecruitmatrix_%s.png",
                  RPlotz$Genus_Code[1],"log"), plot = plotz)
#recruitment
RPlotz <- POSP_R #change this variable

plotz <- ggplot(RPlotz, aes(x=Sites, y=Years)) + 
  geom_raster(aes(fill = Tots_recs_peryear))+ #change fill to look at diff VR functions
  scale_fill_gradient(low = "grey90", high = "purple" )+
  labs(title = sprintf("Recruitment matrix visualization: %s", RPlotz$Genus_Code[1])) + theme_bw() +
  theme(plot.title = element_text(size = 20, face = "bold"), axis.text.x =  element_text(angle = 45, hjust = 1)) 
ggsave(filename = sprintf("Figures/%s_indeprecruitmatrix.png",
                  RPlotz$Genus_Code[1]), plot = plotz)

```

# TO DO
## Devynn
[ ] Add the data limiter part to get rid of sites/intervals with too few transitions
[X] Add area into the recruitment calculations
[X] Run & save all models & interactions
[X] Convert data into the format for matrix visualizations
[ ] Plot recruitment barplots
[ ] Write descriptions & explanations of steps
[X] Put models in IPMs 
[ ] Learn how to do sensitivity analysis


# IGNORE SOME OF THE STUFF BELOW FOR NOW



```{r}
# modS <- glm(survival ~ size, family = "binomial" , data = surv_dat)
plot(jitter(survival, 0.1) ~ size, Choice)
ss <- seq(-3, 9, 0.1)
lines(ss, predict(modS_site[1], list(size = ss), type="response"), pch=8)

summary(modS_site)
summary(modS_year)
summary(modS_site_year)
drop1(modS_site_POCS, test="F")

modS_site_POSP <- glm(survival ~ size + Site, family = "binomial" , 
           data = ColonyLevel[ColonyLevel$Genus_Code == GeneraNames[2],])
summary(modS_site_POSP)
drop1(modS_site_POSP, test="F")

modS_site_MOSP <- glm(survival ~ size + Site, family = "binomial" , 
           data = ColonyLevel[ColonyLevel$Genus_Code == GeneraNames[3],])
summary(modS_site_MOSP)
drop1(modS_site_MOSP, test="F")
```



### Growth 

```{r 1 GeneraMod Growth,}
################################################################################
######### Genera models: Growth ################################################
################################################################################
  
# initializing the data runs for the growth analysis
# define the parms for model loop
Focus <- GeneraNames 
LoopLength <- length(Focus)
minTrans <- 30 # minimum number of transitions

growth <- matrix(0, nrow = 2, ncol = LoopLength)
note <- aic <- Var <- c()

GrowthDataFrame <- data.frame() #initialize 
for (i in 1:LoopLength){
  subset1 <- subset(ColonyLevel, Genus_Code == Focus[i])
  
  
  # subsetting for growth & shrinkage
  subset2 <- subset(subset1, TransitionTypeSimple == "GROWTH" | 
                   TransitionTypeSimple == "SHRINK")
  
  ln_SS <- subset2$ln_SS
  ln_ESc <- subset2$ln_ESc
  
  # Saving growth model
  if (length(ln_SS) >= minTrans){
    mod <- lm(ln_ESc ~ ln_SS)
    note[i] <- sprintf("Num of transitions = %s", 
                    length(ln_SS))
    
    growth[,i] <- coef(mod)
    Var[i] <- (summary(mod)$sigma)**2
    aic[i] <- AIC(mod)
    }
  
  if (length(ln_SS) < minTrans){
    #setting values to NaNs
    note[i] <- sprintf("Not enough data. Num transitions = %s", 
                    length(ln_SS))
    growth[,i] <- NaN
    Var[i] <- NA
    aic[i] <- NA
    }
  
  # Row binding the model results into the growth model dataframe
  
  df <- data.frame(Model_IDs = sprintf("%s_All_Sites_n_Years",Focus[i]), 
                 g.int = growth[1,i], g.slp = growth[2,i], g.var = Var[i], 
                 AIC = aic[i], growth_notes = note[i])
  
  GrowthDataFrame <- rbind(GrowthDataFrame,df)
}


```


```{r 2 SiteMod Growth,}
################################################################################
######### Site models ##########################################################
################################################################################

# initializing the data runs for the growth analysis
# define the parms for model loop
Focus <- SiteNames 
LoopLength <- length(Focus)
minTrans <- 30 # minimum number of transitions

growth <- matrix(0, nrow = 2, ncol = LoopLength)
Var <- aic <- note <- c()

for (i in 1:LoopLength){
  subset1 <- subset(ColonyLevel, Site == Focus[i])
  
  # subsetting for growth & shrinkage
  subset2 <- subset(subset1, TransitionTypeSimple == "GROWTH" | 
                   TransitionTypeSimple == "SHRINK")
  
  ln_SS <- subset2$ln_SS
  ln_ESc <- subset2$ln_ESc
  
  if (length(ln_SS) > minTrans){
    mod <- lm(ln_ESc ~ ln_SS)
    note[i] <- sprintf("Num of transitions = %s", length(ln_SS))
    
    growth[,i] <- coef(mod)
    Var[i] <- (summary(mod)$sigma)**2
    aic[i] <- AIC(mod)}
  
  if (length(ln_SS) <= minTrans){
    #setting values to NaNs
    note[i] <- sprintf("Not enough data. Num transitions = %s", 
                    length(ln_SS))
    growth[,i] <- NaN
    Var[i] <- NA
    aic[i] <- NA}

  # saving the growth model
  df <- data.frame(Model_IDs = sprintf("%s_All_Genera_n_Years",Focus[i]), 
                 g.int = growth[1,i], g.slp = growth[2,i], 
                 g.var = Var[i], AIC = aic[i], growth_notes = note[i])
  
  GrowthDataFrame <- rbind(GrowthDataFrame,df)
}

```


```{r 3 YearMod Growth,}
################################################################################
######### Interval Year models #################################################
################################################################################

# initializing the data runs for the growth analysis
# define the parms for model loop
Focus <- IntervalYears 
LoopLength <- length(Focus)
minTrans <- 30 # minimum number of colonies

growth <- matrix(0, nrow = 2, ncol = LoopLength)
Var <- note <- aic <- c()
 
for (i in 1:LoopLength){
  subset1 <- subset(ColonyLevel, Interval == Focus[i])
  
  # subsetting for growth & shrinkage
  subset2 <- subset(subset1, TransitionTypeSimple == "GROWTH" | 
                   TransitionTypeSimple == "SHRINK")
  
  ln_SS <- subset2$ln_SS
  ln_ESc <- subset2$ln_ESc
  
  if (length(ln_SS) > minTrans){
    mod <- lm(ln_ESc ~ ln_SS)
    note[i] <- sprintf("Num of transitions = %s", length(ln_SS))
    
    growth[,i] <- coef(mod)
    Var[i] <- (summary(mod)$sigma)**2
    aic[i] <- AIC(mod)}
  
  if (length(ln_SS) <= minTrans){
    #setting values to NaNs
    note[i] <- sprintf("Not enough data. Num transitions = %s", 
                    length(ln_SS))
    growth[,i] <- NaN
    Var[i] <- NA
    aic[i] <- NA}
  
  df <- data.frame(Model_IDs = sprintf("%s_All_Genera_n_Sites",Focus[i]), 
                 g.int = growth[1,i], g.slp = growth[2,i], 
                 g.var = Var[i], AIC = aic[i], growth_notes = note[i])
  
  GrowthDataFrame <- rbind(GrowthDataFrame,df)
}

```
```{r 4 Genera + Site Mod Growth,}
################################################################################
######### Genera + Site for all Interval Years models: growth ##################
################################################################################

# define the parms for model loop
# Now with a second "Focus"
Focus <- GeneraNames
subFocus <- SiteNames
LoopLength <- length(Focus)
LoopLengthSF <-  length(subFocus)

# setting minimum number of colonies
minTrans <- 30 

for (i in 1:LoopLength){
  
  # redefine the matrix for each Focus step
  growth <- matrix(0, nrow = 2, ncol = LoopLengthSF)
  note <- Var <- aic <- c()
  
  # subset ColonyLevel to specify first focus
  subset1 <- subset(ColonyLevel, Genus_Code == Focus[i])
  
  for (v in 1:LoopLengthSF){
    # subsetting for growth & shrinkage
    subset2 <- subset(subset1, TransitionTypeSimple == "GROWTH" | 
                 TransitionTypeSimple == "SHRINK")
    
    # subsetting growth & shrinkage for second focus
    subset3 <- subset(subset2, Site == subFocus[v])
    
    ln_SS <- subset3$ln_SS
    ln_ESc <- subset3$ln_ESc
    
    if (length(ln_SS) > minTrans){
      mod <- lm(ln_ESc ~ ln_SS)
      note[v] <- sprintf("Num of transitions = %s", length(ln_SS))
      growth[,v] <- coef(mod)
      Var[v] <- (summary(mod)$sigma)**2
      aic[v] <- AIC(mod)}
    
    if (length(ln_SS) <= minTrans){
      #setting values to NaNs
      note[v] <- sprintf("Not enough data. Num transitions = %s", 
                      length(ln_SS))
      growth[,v] <- NaN
      Var[v] <- NA
      aic[v] <- NA}
    
  df <- data.frame(Model_IDs = sprintf("%s_%s_All_Years",Focus[i], subFocus[v]), 
                 g.int = growth[1,v], g.slp = growth[2,v], 
                 g.var = Var[v], AIC = aic[v], growth_notes = note[v])
  
  GrowthDataFrame <- rbind(GrowthDataFrame,df)
  
  }} 
 
```
```{r 5 Genera + Years Mod Growth,}
################################################################################
######### Genera + Interval Years for all Site models ##########################
################################################################################

# define the parms for model loop
# Now with a second "Focus"

Focus <- GeneraNames
subFocus <- IntervalYears
LoopLength <- length(Focus)
LoopLengthSF <-  length(subFocus)

# setting minimum number of transitions
minTrans <- 30 

for (i in 1:LoopLength){
  
  # redefine the matrix for each Focus step
  growth <- matrix(0, nrow = 2, ncol = LoopLengthSF)
  survival <- growth
  note <- Var <- aic <- c()
  Snote <- Var_S <- aic_S <- c()
  
  # subset data frames to specify first focus
  subset1 <- subset(ColonyLevel, Genus_Code == Focus[i])

  for (v in 1:LoopLengthSF){
    
    # subsetting for growth & shrinkage
    subset2 <- subset(subset1, TransitionTypeSimple == "GROWTH" | 
                 TransitionTypeSimple == "SHRINK")
    
    # subsetting growth & shrinkage for second focus
    subset3 <- subset(subset2, Interval == subFocus[v])
    
    ln_SS <- subset3$ln_SS
    ln_ESc <- subset3$ln_ESc

    if (length(ln_SS) > minTrans){
      mod <- lm(ln_ESc ~ ln_SS)
      note[v] <- sprintf("Num of transitions = %s", length(ln_SS))
      growth[,v] <- coef(mod)
      Var[v] <- (summary(mod)$sigma)**2
      aic[v] <- AIC(mod)}
    
    if (length(ln_SS) <= minTrans){
      #setting values to NaNs
      note[v] <- sprintf("Not enough data. Num transitions = %s", 
                      length(ln_SS))
      growth[,v] <- NaN
      Var[v] <- NA
      aic[v] <- NA}
    
    df <- data.frame(Model_IDs = sprintf("%s_%s_All_Sites",Focus[i], subFocus[v]), 
               g.int = growth[1,v], g.slp = growth[2,v], 
               g.var = Var[v], AIC = aic[v], growth_notes = note[v])
  
    GrowthDataFrame <- rbind(GrowthDataFrame,df)
  
}}
 
```
```{r 6 Site + Years Mod Growth,}
################################################################################
######### Site + Interval Years for all Genera models ##########################
################################################################################

# define the parms for model loop
# Now with a second "Focus"

Focus <-SiteNames
subFocus <- IntervalYears
LoopLength <- length(Focus)
LoopLengthSF <-  length(subFocus)

# setting minimum number of transitions
minTrans <- 30 

for (i in 1:LoopLength){
  
  # redefine the matrix for each Focus step
  growth <- matrix(0, nrow = 2, ncol = LoopLengthSF)
  survival <- growth
  note <- Var <- aic <- c()
  Snote <- Var_S <- aic_S <- c()
  
  # subset ColonyLevel to specify first focus
  subset1 <- subset(ColonyLevel, Site == Focus[i])


  for (v in 1:LoopLengthSF){
    
    # subsetting for growth & shrinkage
    subset2 <- subset(subset1, TransitionTypeSimple == "GROWTH" | 
                 TransitionTypeSimple == "SHRINK")
    
    # subsetting for Interval_Years
    subset3 <- subset(subset2, Interval == subFocus[v])
    
    ln_SS <- subset3$ln_SS
    ln_ESc <- subset3$ln_ESc
    
    if (length(ln_SS) > minTrans){
      mod <- lm(ln_ESc ~ ln_SS)
      note[v] <- sprintf("Num of transitions = %s", length(ln_SS))
      growth[,v] <- coef(mod)
      Var[v] <- (summary(mod)$sigma)**2
      aic[v] <- AIC(mod)}
    
    if (length(ln_SS) <= minTrans){
      #setting values to NaNs
      note[v] <- sprintf("Not enough data. Num transitions = %s", 
                      length(ln_SS))
      growth[,v] <- NaN
      Var[v] <- NA
      aic[v] <- NA}
    
    # saving growth model 
    
    df <- data.frame(Model_IDs = sprintf("%s_%s_All_Genera",Focus[i], subFocus[v]), 
             g.int = growth[1,v], g.slp = growth[2,v], 
             g.var = Var[v], AIC = aic[v], growth_notes = note[v])
  
    GrowthDataFrame <- rbind(GrowthDataFrame,df)
  }}
```




### Survival

```{r 1 GeneraMod Survival,}
################################################################################
######### Genera models: Survival ##############################################
################################################################################
SurvivalDataFrame <- data.frame()

Focus <- GeneraNames 
LoopLength <- length(Focus)
minTrans <- 30 # minimum number of transitions
survival <- matrix(0, nrow = 2, ncol = LoopLength)
Snote <- aic_S  <- c()

for (i in 1:LoopLength){
  subset1_S <- subset(ColonyLevel, Genus_Code == Focus[i])
# Saving survival model
  
  if (length(subset1_S$size) >= minTrans){
    modS <- glm(survival ~ size, family = "binomial" , data = subset1_S)
    Snote[i] <- sprintf("Num of transitions = %s", 
                    length(subset1_S$size))
    
    survival[,i] <- coef(modS)
    aic_S[i] <- AIC(modS)
    }
  
  if (length(subset1_S$size) < minTrans){
    #setting values to NaNs
    Snote[i] <- sprintf("Not enough data. Num transitions = %s", 
                    length(subset1_S$size))
    survival[,i] <- NaN
    aic_S[i] <- NA
  }
  
  # Row binding the model results into the growth model dataframe
  
  dfS <- data.frame(Model_IDs = sprintf("%s_All_Sites_n_Years",Focus[i]), 
                                s.int = survival[1,i], s.slp = survival[2,i], 
                                AIC = aic_S[i], survival_notes = Snote[i])
  
  SurvivalDataFrame <- rbind(SurvivalDataFrame,dfS)
  
}

# the model does converge here  

 
```
```{r 2 SiteMod Survival,}
################################################################################
######### Site models: Survival ################################################
################################################################################

# initializing the data runs for the growth analysis
# define the parms for model loop
Focus <- SiteNames 
LoopLength <- length(Focus)
minTrans <- 30 # minimum number of transitions

survival <- matrix(0, nrow = 2, ncol = LoopLength)
Snote <- aic_S <- c()

for (i in 1:LoopLength){
  subset1_S <- subset(ColonyLevel, Site == Focus[i])
  
  if (length(subset1_S$size) >= minTrans){
    modS <- glm(survival ~ size, family = "binomial" , data = subset1_S)
    Snote[i] <- sprintf("Num of transitions = %s", 
                    length(subset1_S$size))
    
    survival[,i] <- coef(modS)
    aic_S[i] <- AIC(modS)
    }
  
  if (length(subset1_S$size) < minTrans){
    #setting values to NaNs
    Snote[i] <- sprintf("Not enough data. Num transitions = %s", 
                    length(subset1_S$size))
    survival[,i] <- NaN
    Var_S[i] <- NA
    aic_S[i] <- NA
    }
  

 # Row binding the model results into the growth model dataframe
  
  dfS <- data.frame(Model_IDs = sprintf("%s_All_Genera_n_Years",Focus[i]), 
                                s.int = survival[1,i], s.slp = survival[2,i], 
                                AIC = aic_S[i], survival_notes = Snote[i])
  
  SurvivalDataFrame <- rbind(SurvivalDataFrame,dfS)
  }

## Getting the error: "glm.fit: algorithm did not converge" might need to start this loop with a new dataframe for the survival data? 
```
```{r 3 YearMod Survival,}
################################################################################
########## Interval Year models: survival ######################################
################################################################################

# initializing the data runs for the growth analysis
# define the parms for model loop
Focus <- IntervalYears 
LoopLength <- length(Focus)
minTrans <- 30 # minimum number of colonies

survival <- matrix(0, nrow = 2, ncol = LoopLength)
Snote <- aic_S <- c()

for (i in 1:LoopLength){
  subset1_S <- subset(ColonyLevel, Interval == Focus[i])
  
   # Survival model 
  if (length(subset1_S$size) >= minTrans){
    modS <- glm(survival ~ size, family = "binomial" , data = subset1_S)
    Snote[i] <- sprintf("Num of transitions = %s", 
                    length(subset1_S$size))
    
    survival[,i] <- coef(modS)
    aic_S[i] <- AIC(modS)
    }
  
  if (length(subset1_S$size) < minTrans){
    #setting values to NaNs
    Snote[i] <- sprintf("Not enough data. Num transitions = %s", 
                    length(subset1_S$size))
    survival[,i] <- NaN
    aic_S[i] <- NA
    }
  

  # Row binding the model results into the growth model dataframe
  
  dfS <- data.frame(Model_IDs = sprintf("%s_All_Genera_n_Sites",Focus[i]), 
                                s.int = survival[1,i], s.slp = survival[2,i], 
                                AIC = aic_S[i], survival_notes = Snote[i])
  
  SurvivalDataFrame <- rbind(SurvivalDataFrame,dfS)
  
}

## Getting the error: "glm.fit: algorithm did not converge" might need to start this loop with a new dataframe for the survival data? 
```
```{r 4 Genera + Site Mod Survival,}
################################################################################
######### Genera + Site for all Interval Years models: survival ################
################################################################################

# define the parms for model loop
Focus <- GeneraNames
subFocus <- SiteNames
LoopLength <- length(Focus)
LoopLengthSF <-  length(subFocus)

# setting minimum number of colonies
minTrans <- 30 

for (i in 1:LoopLength){
  survival <- matrix(0, nrow = 2, ncol = LoopLengthSF)
  Snote <- aic_S <- c()

  subset1_S <- ColonyLevel[ColonyLevel$Genus_Code == Focus[i],]

  for (v in 1:LoopLengthSF){
    #v = 8
    subset2_S <- subset1_S[subset1_S$Site == subFocus[v],]
    
    if (nrow(subset2_S) == 0){
      #setting values to NaNs
    Snote[v] <- sprintf("No data for %s and %s", Focus[i], subFocus[v])
    survival[,v] <- NaN
    aic_S[v] <- NA
    }
    
    if (length(subset2_S$size) >= minTrans){
    modS <- glm(survival ~ size, family = "binomial" , data = subset2_S)
    Snote[v] <- sprintf("Num of patches = %s", 
                    length(subset2_S$size))
    
    survival[,v] <- coef(modS)
    aic_S[v] <- AIC(modS)
    }
  
  if (length(subset2_S$size) < minTrans){
    #setting values to NaNs
    Snote[v] <- sprintf("Not enough data. Num patches = %s", 
                    length(subset2_S$size))
    survival[,v] <- NaN
    aic_S[v] <- NA
    }
  
  
  dfS <- data.frame(Model_IDs = sprintf("%s_All_Years",Focus[v]), 
                                s.int = survival[1,v], s.slp = survival[2,v], 
                                AIC = aic_S[v], survival_notes = Snote[v])
  
  SurvivalDataFrame <- rbind(SurvivalDataFrame,dfS)
   
   
  }
}

```
```{r 5 Genera + Years Mod Survival,}
################################################################################
######### Genera + Interval Years for all Site models ##########################
################################################################################

# define the parms for model loop
# Now with a second "Focus"

Focus <- GeneraNames
subFocus <- IntervalYears
LoopLength <- length(Focus)
LoopLengthSF <-  length(subFocus)

# setting minimum number of transitions
minTrans <- 30 

for (i in 1:LoopLength){
  
  # redefine the matrix for each Focus step
  survival <- matrix(0, nrow = 2, ncol = LoopLengthSF)
  Snote <- aic_S <- c()
  
  # subset data frames to specify first focus
  subset1_S <- subset(ColonyLevel, Genus_Code == Focus[i])

  for (v in 1:LoopLengthSF){

    # subsetting growth & shrinkage for second focus
    subset2_S <- subset(subset1_S, Interval == subFocus[v])
    
    # Survival model 
    if (length(subset2_S$size) >= minTrans){
      modS <- glm(survival ~ size, family = "binomial" , data = subset2_S)
      Snote[v] <- sprintf("Num of transitions = %s", 
                      length(subset2_S$size))
      
      survival[,v] <- coef(modS)
      aic_S[v] <- AIC(modS)
      }
    
    if (length(subset2_S$size) < minTrans){
      #setting values to NaNs
      Snote[v] <- sprintf("Not enough data. Num transitions = %s", 
                      length(subset2_S$size))
      survival[,v] <- NaN
      aic_S[v] <- NA
      }
    
  
    # Row binding the model results into the growth model dataframe
    
    dfS <- data.frame(Model_IDs = sprintf("%s_All_Sites",Focus[v]), 
                                  s.int = survival[1,v], s.slp = survival[2,v], 
                                  AIC = aic_S[v], survival_notes = Snote[v])
    
    SurvivalDataFrame <- rbind(SurvivalDataFrame,dfS)
  }

}

```
```{r 6 Site + Years Mod Survival,}
################################################################################
######### Site + Interval Years for all Genera models ##########################
################################################################################

# define the parms for model loop
# Now with a second "Focus"

Focus <-SiteNames
subFocus <- IntervalYears
LoopLength <- length(Focus)
LoopLengthSF <-  length(subFocus)

# setting minimum number of transitions
minTrans <- 30 

for (i in 1:LoopLength){
  
  # redefine the matrix for each Focus step
  survival <- matrix(0, nrow = 2, ncol = LoopLengthSF)
  Snote<- aic_S <- c()
  
  # subset ColonyLevel to specify first focus
  subset1 <- subset(ColonyLevel, Site == Focus[i])

  for (v in 1:LoopLengthSF){
    
    # subsetting for Interval
    subset2_S <- subset(subset1_S, Interval == subFocus[v])

    # Survival model 
    if (length(subset2_S$size) >= minTrans){
      modS <- glm(survival ~ size, family = "binomial" , data = subset2_S)
      Snote[v] <- sprintf("Num of transitions = %s", 
                      length(subset2_S$size))
      
      survival[,v] <- coef(modS)
      aic_S[v] <- AIC(modS)
      }
    
    if (length(subset2_S$size) < minTrans){
      #setting values to NaNs
      Snote[v] <- sprintf("Not enough data. Num transitions = %s", 
                      length(subset2_S$size))
      survival[,v] <- NaN
      aic_S[v] <- NA
      }
    
  
    # Row binding the model results into the survival model dataframe
    
    dfS <- data.frame(Model_IDs = sprintf("%s_All_Genera",Focus[v]), 
                                  s.int = survival[1,v], s.slp = survival[2,v], 
                                  AIC = aic_S[v], survival_notes = Snote[v])
    
    SurvivalDataFrame <- rbind(SurvivalDataFrame,dfS)
     
  
  }

}


```


```{r}
# define the parms for model loop
Focus <- GeneraNames 
LoopLength <- length(Focus)

recruit_genera <- matrix(NaN, nrow = length(IntervalYears), ncol = LoopLength)

# These all depend on the interval years so it doesn't totally makes sense to get a model for that since we want a yearly recruitment rate.

# Calculate the rec vals for each genera at all sites
# Separate each genera 
# - for each unique interval year, take the sum of the area before recuritment (StartingSize)
# - get the num of recurites for each unique interval year
# - num rec / area * interval year (recruit/area*year)
# - should have 3 numbers
# Can leave it as vector for interval years or take an average...?

for (i in 1:LoopLength){

  subset1 <- subset(ColonyLevel, Genus_Code == Focus[i])
  
  #calculate unique time intervals
  timeint_all <- unique(subset1$Interval_Years)
  
  rec <- c()
  area <- rep(0,length(timeint_all)) #initalize vector
  for (w in 1:length(timeint_all)){
  area[w] <- sum(subset1$StartingSize[which(subset1$Interval_Years ==
                                              timeint_all[w])])
  if (area[w] == 0) area[w]<- NA
  rec[w] <- sum(subset1$Recruit[which(subset1$Interval_Years ==
                                              timeint_all[w])])}
  
  rec <- rec / area * timeint_all # this is the number multiplied by the total area at each time step to give the number of recurits at the following time step.
  
  recruit_genera[(1:length(rec)),i] <- rec
}

# Calculate the rec vals for each site all genera together
# -similar process as above, should have 11 #s
# define the parms for model loop
Focus <- SiteNames 
LoopLength <- length(Focus)

recruit_site <- matrix(NaN, nrow = length(IntervalYears), ncol = LoopLength)
for (i in 1:LoopLength){

  subsetz <- subset(ColonyLevel, Site == Focus[i])
  
  #calculate unique time intervals
  timeint_all <- unique(subsetz$Interval_Years)
  
  rec <- c()
  area <- rep(0,length(timeint_all)) #initalize vector
  for (w in 1:length(timeint_all)){
  area[w] <- sum(subsetz$StartingSize[which(subsetz$Interval_Years ==
                                              timeint_all[w])])
  if (area[w] == 0) area[w]<- NA
  rec[w] <- sum(subsetz$Recruit[which(subsetz$Interval_Years ==
                                              timeint_all[w])])}
  
  rec <- rec / area * timeint_all # this is the number multiplied by the total area at each time step to give the number of recurits at the following time step.
  
  recruit_site[(1:length(rec)),i] <- rec
}
# Calculate the rec vals for each site and each genera there
# - similar to before but with 33 possible values (not all sites had recruits for some genera)
Focus <- GeneraNames
subFocus <- SiteNames
LoopLength <- length(Focus)
LoopLengthSF <- length(subFocus)

recruit_sitegenera <- data.frame()

for (t in 1:LoopLength){
  recruit <- matrix(NaN, nrow = length(IntervalYears), ncol = LoopLengthSF)
  
  subseta <- subset(ColonyLevel, Genus_Code == Focus[t])
  
  for( i in 1:LoopLengthSF){
    
    subsetz <- subseta[subseta$Site == subFocus[i],]
    #calculate unique time intervals
    timeint_all <- unique(subsetz$Interval_Years)
    
    rec <- c()
    area <- rep(0,length(timeint_all)) #initalize vector
    
    if (nrow(subsetz) == 0) rec <- NaN
    
    else{  
      rec[w] <- sum(subsetz$Recruit[which(subsetz$Interval_Years ==
                                                timeint_all[w])])
      for (w in 1:length(timeint_all)){
      area[w] <- sum(subsetz$StartingSize[which(subsetz$Interval_Years ==
                                                timeint_all[w])])
      }
      rec <- rec / area * timeint_all
    }
     # this is the number multiplied by the total area at each time step to give the number of recurits at the following time step.
    
    recruit[(1:length(rec)),i] <- rec
  }
  recruit_sitegenera <- rbind(recruit_sitegenera, data.frame(Genus_Code = GeneraNames[t], rec_info = recruit))
}
View(recruit_sitegenera)

```


#Bar plots for reproduction
```{r,}
allrecs <- data.frame()

for (i in 1:length(GeneraNames)){
  ByGen <- subset(ColonyLevel, Genus_Code == GeneraNames[i])
  site <-  unique(ByGen$Site)
  for (l in 1:length(site)) {
    recs <- c()
    l = 1
    intz <- unique(ByGen$Interval)
    
    recs[l] <- sum(ByGen$Recruit[which(ByGen$Site == site[l])])
    allrecs <- rbind(allrecs, data.frame(Genera = sprintf("%s", GeneraNames[i]),
                                         siteInterval=sprintf("%s", siteInt[l]),
                                         rec_vals = recs[l]))
  }}

barplot(allrecs[allrecs$Genera == GeneraNames[1],][[3]], width = 0.5,
        names.arg = allrecs[allrecs$Genera == GeneraNames[1],][[2]], 
        main = GeneraNames[1], ylab = "Total recruits")

barplot(allrecs[allrecs$Genera == GeneraNames[2],][[3]], width = 0.5,
        names.arg = allrecs[allrecs$Genera == GeneraNames[2],][[2]],
        main = GeneraNames[2], ylab = "Total recruits")

barplot(allrecs[allrecs$Genera == GeneraNames[3],][[3]], width = 0.5,
        names.arg = allrecs[allrecs$Genera == GeneraNames[3],][[2]],
        main = GeneraNames[3], ylab = "Total recruits")

```


```{r}
#if the time interval is less than 1 year, need to drop them!!!

# sum number of recruits/site

recruit_bar <- data.frame()

for (i in 1:length(GeneraNames)){
  subsetz1 <- subset(ColonyLevel, Genus_Code == GeneraNames[i])

  for (l in 1:length(SiteNames)) {
    subsetz2 <- subsetz1[subsetz1$Site == SiteNames[i],]

    timeint <- unique(subsetz2$Interval)
    numbrecruits <- c()
    
    for (w in 1:length(timeint)){
      numbrecruits[w] <- sum(subsetz2$Recruit[which(subsetz2$Interval ==
                                            timeint[w])])
    }
    print(numbrecruits)
    print(timeint)
    
    # cat <- data.frame(ID=sprintf("%s_%s",GeneraNames[i],SiteNames[l]), Mean = 
    #                     mean(numbrecruits), 
    #                   StdError= sd(numbrecruits)/sqrt(length(numbrecruits)))
    # recruit_bar <- rbind(recruit_bar,cat)
  }
}


  for (i in 1:length(SiteNames)){
  recruit_bar <- matrix(NaN, nrow = length(IntervalYears), ncol = length(SiteNames))
  subsetz <- subset(ColonyLevel, Site == SiteNames[i])
  
  #calculate unique time intervals
  timeint_all <- unique(subsetz$Interval_Years)
  #for every interval year, get the sum of the number of recruits
  rec <- c()
  numbrecruits <- rep(0,length(timeint_all)) #initalize vector
  for (w in 1:length(timeint_all)){
  numbrecruits[w] <- sum(subsetz$Recruit[which(subsetz$Interval_Years ==
                                              timeint_all[w])])
  if (numbrecruits[w] == 0) numbrecruits[w]<- NA
  }
  
  rec <- numbrecruits * timeint_all # this is the # of recruits at each time step to give the number of recurits at the following time step.
  
  recruit_bar[(1:length(rec)),i] <- rec
  
  #row bind results into recruit #s dataframe
  rec_bar <- rbind(recruit_bar, data.frame(SiteName = SiteNames[i]))
}
View(recruit_bar)

```


Caroline Plotting
#final data?
Regional Growth plots
```{r}
load("data/Colony_Data_20210917_edited.rdata") 
load("data/all_RegionalLambdas_120321.rdata") 

#need to change all the GrowthRegionalDF to ModelParams_Regional

#all growth
  ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK") & REGION=="NWHI") %>%
    ggplot(aes(x=log10_SS, y=log10_ESc))+
    geom_point()+ geom_abline(intercept = 0)+
    #geom_abline(intercept = GrowthRegionalDF$g.int[5], slope = GrowthRegionalDF$g.slp[5],color="blue")+
    ggtitle(paste0("Growth fit at all sites + all interval years in ",GrowthRegionalDF$REGION[4]))
  
  
  PlotNum = 2
  posp <- ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK") & Genus_Code=="POSP" & REGION=="NWHI" ) %>% #change genus code/region for each plot
    ggplot(aes(x=log10_SS, y=log10_ESc))+
    #geom_point(color="red")+ 
    geom_abline(intercept = 0)+
    geom_abline(intercept = GrowthRegionalDF$g.int[PlotNum], slope = GrowthRegionalDF$g.slp[PlotNum],color="red", linetype="dashed" )+
    ggtitle(paste0("Porites growth fit all sites/intervals"))+
    theme_bw()+
    theme(legend.position = "none",legend.title = element_blank())+
    xlim(c(0,4))+ylim(c(-2,4))+
    xlab("Log Size (time = T)")+ ylab("Log Size (time = T+1")+
    annotate("text",x=1,y=4, color="red", label=paste0("y = ",round(GrowthRegionalDF$g.slp[PlotNum],2),"x + ",round(GrowthRegionalDF$g.int[PlotNum],3)) )+
    scale_color_brewer()
  
  PlotNum = 1
  mosp <- ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK") & Genus_Code=="MOSP" & REGION=="NWHI" ) %>% #change genus code/region for each plot
    ggplot(aes(x=log10_SS, y=log10_ESc))+
    geom_point(color="red")+ geom_abline(intercept = 0)+
    geom_abline(intercept = GrowthRegionalDF$g.int[PlotNum], slope = GrowthRegionalDF$g.slp[PlotNum],color="red", linetype="dashed" )+
    ggtitle(paste0("Montipora growth fit all sites/intervals"))+
    theme_bw()+
    theme(legend.position = "none",legend.title = element_blank())+
    xlim(c(0,4))+ylim(c(-2,4))+
    xlab("Log Size (time = T)")+ ylab("Log Size (time = T+1")+
    annotate("text",x=1,y=4, color="red", label=paste0("y = ",round(GrowthRegionalDF$g.slp[PlotNum],2),"x + ",round(GrowthRegionalDF$g.int[PlotNum],3)) )+
    scale_color_brewer()
  
  PlotNum = 3
  pocs <- ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK") & Genus_Code=="POCS" & REGION=="NWHI" ) %>% #change genus code/region for each plot
    ggplot(aes(x=log10_SS, y=log10_ESc))+
    geom_point(color="red")+ geom_abline(intercept = 0)+
    geom_abline(intercept = GrowthRegionalDF$g.int[PlotNum], slope = GrowthRegionalDF$g.slp[PlotNum],color="red", linetype="dashed" )+
    ggtitle(paste0("Pocillopora growth fit all sites/intervals"))+
    theme_bw()+
    theme(legend.position = "none",legend.title = element_blank())+
    xlim(c(0,4))+ylim(c(-2,4))+
    xlab("Log Size (time = T)")+ ylab("Log Size (time = T+1")+
    annotate("text",x=1,y=4, color="red", label=paste0("y = ",round(GrowthRegionalDF$g.slp[PlotNum],2),"x + ",round(GrowthRegionalDF$g.int[PlotNum],3)) )+
    scale_color_brewer()
  
  posp + mosp + pocs

#mean growth rate by region and genus
ColonyLevel %>% 
  filter(TransitionTypeSimple %in% c("GROWTH","SHRINK")) %>%
  select(SEC_NAME,Genus_Code,REGION,TransitionRate_L)%>%
  group_by(Genus_Code,REGION) %>% 
  summarise(meangrow = mean(TransitionRate_L)
    
  )
  
```

Regional survival plots
```{r}

#take int and slp from ModelParams and add them as predict lines
#y needs to be survival probability
#need to jitter survival data

# library(survminer)
# library(survival)
# testing <- ColonyLevel %>% 
#     filter(TransitionTypeSimple %in% c("GROWTH","SHRINK","MORT") & Genus_Code=="POCS" & REGION=="NWHI" )
# fit <- survfit(Surv(log10_SS)~Genus_Code, data = testing)
# ggsurvplot(fit, data = testing)


load("data/Colony_Data_202100917_edited_survival.rdata") #surv_dat
head(surv_dat)

# plot(jitter(survival,0.1) ~ size, surv_dat
#      )
# ss <- seq(-3, 9, 0.1)
# lines(ss, predict(slope=RegionalAnnSurvDataFrame$s.slp[1], intercept=RegionalAnnSurvDataFrame$s.int[1], list(ln_SS = ss), type="response"), pch=8)

scurve <- function(x){
  y <- exp(x) / (1 + exp(x))
  return(y)
}
ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK","MORT") & Genus_Code=="MOSP" &
             REGION=="MHI" )%>%  #change genus code/region for each plot
ggplot(aes(x=log10_SS, y=Survival)) + geom_point(position=position_jitter(height=0.03, width=0))+
  stat_function(fun = scurve, n = 100)



##############
#MHI


#MOSP
PlotNum = 5 #change based on region
mosp <- ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK","MORT") & Genus_Code=="MOSP" &
             REGION=="MHI" )%>%  #change region for each plot
  ggplot(aes(x=log10_SS, y=Survival)) + geom_point(position=position_jitter(height=0.03, width=0))+
  stat_smooth(method = "glm",method.args = list(family="binomial"),color="blue" )+ #remove se=FALSE if don't want error around line
  ggtitle(paste0("Montipora survival fit all sites/intervals"))+
  theme_bw()+
  xlim(c(-1,5))+
  xlab("Log Size (time = T)")+ ylab("Survival probability")+
  annotate("text",x=3,y=0.25, color="blue", 
           label=paste0("slope = ",round(ModelParams_Regional$s.slp[PlotNum],2),"\n ","intercept =  ",round(ModelParams_Regional$s.int[PlotNum],2)) )

#POSP
PlotNum = 4
posp <- ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK","MORT") & Genus_Code=="POSP" &
             REGION=="MHI" )%>%  #change region for each plot
  ggplot(aes(x=log10_SS, y=Survival)) + geom_point(position=position_jitter(height=0.03, width=0))+
  stat_smooth(method = "glm",method.args = list(family="binomial"),color="blue" )+ #remove se=FALSE if don't want error around line
  ggtitle(paste0("Porites survival fit all sites/intervals"))+
  theme_bw()+
  xlim(c(-1,5))+
  xlab("Log Size (time = T)")+ ylab("Survival probability")+
  annotate("text",x=3,y=0.25, color="blue", 
           label=paste0("slope = ",round(ModelParams_Regional$s.slp[PlotNum],2),"\n ","intercept =  ",round(ModelParams_Regional$s.int[PlotNum],2)) )


#POCS
PlotNum = 6
pocs <- ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK","MORT") & Genus_Code=="POCS" &
             REGION=="MHI" )%>%  #change region for each plot
  ggplot(aes(x=log10_SS, y=Survival)) + geom_point(position=position_jitter(height=0.03, width=0))+
  stat_smooth(method = "glm",method.args = list(family="binomial"),color="blue" )+ #remove se=FALSE if don't want error around line
  ggtitle(paste0("Pocillopora survival fit all sites/intervals"))+
  theme_bw()+
  xlim(c(-1,5))+
  xlab("Log Size (time = T)")+ ylab("Survival probability")+
  annotate("text",x=3,y=0.25, color="blue", 
           label=paste0("slope = ",round(ModelParams_Regional$s.slp[PlotNum],2),"\n ","intercept =  ",round(ModelParams_Regional$s.int[PlotNum],2)) )


posp + mosp + pocs


##############
#NWHI


#MOSP
PlotNum = 1 
mosp <- ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK","MORT") & Genus_Code=="MOSP" &
             REGION=="NWHI" )%>%
  ggplot(aes(x=log10_SS, y=Survival)) + geom_point(position=position_jitter(height=0.03, width=0))+
  stat_smooth(method = "glm",method.args = list(family="binomial"),color="red" )+ #remove se=FALSE if don't want error around line
  ggtitle(paste0("Montipora survival fit all sites/intervals"))+
  theme_bw()+
  xlim(c(-1,5))+
  xlab("Log Size (time = T)")+ ylab("Survival probability")+
  annotate("text",x=3,y=0.25, color="red", 
           label=paste0("slope = ",round(ModelParams_Regional$s.slp[PlotNum],2),"\n ","intercept =  ",round(ModelParams_Regional$s.int[PlotNum],2)) )

#POSP
PlotNum = 2
posp <- ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK","MORT") & Genus_Code=="POSP" &
             REGION=="NWHI" )%>%  #change region for each plot
  ggplot(aes(x=log10_SS, y=Survival)) + geom_point(position=position_jitter(height=0.03, width=0))+
  stat_smooth(method = "glm",method.args = list(family="binomial"),color="red" )+ #remove se=FALSE if don't want error around line
  ggtitle(paste0("Porites survival fit all sites/intervals"))+
  theme_bw()+
  xlim(c(-1,5))+
  xlab("Log Size (time = T)")+ ylab("Survival probability")+
  annotate("text",x=3,y=0.25, color="red", 
           label=paste0("slope = ",round(ModelParams_Regional$s.slp[PlotNum],2),"\n ","intercept =  ",round(ModelParams_Regional$s.int[PlotNum],2)) )


#POCS
PlotNum = 3
pocs <- ColonyLevel %>% 
    filter(TransitionTypeSimple %in% c("GROWTH","SHRINK","MORT") & Genus_Code=="POCS" &
             REGION=="NWHI" )%>%  #change region for each plot
  ggplot(aes(x=log10_SS, y=Survival)) + geom_point(position=position_jitter(height=0.03, width=0))+
  stat_smooth(method = "glm",method.args = list(family="binomial"),color="red" )+ #remove se=FALSE if don't want error around line
  ggtitle(paste0("Pocillopora survival fit all sites/intervals"))+
  theme_bw()+
  xlim(c(-1,5))+
  xlab("Log Size (time = T)")+ ylab("Survival probability")+
  annotate("text",x=3,y=0.25, color="red", 
           label=paste0("slope = ",round(ModelParams_Regional$s.slp[PlotNum],2),"\n ","intercept =  ",round(ModelParams_Regional$s.int[PlotNum],2)) )


posp + mosp + pocs


```



#Recruitment plotting
```{r}
site <- ggplot(ModelParams_SIG_Enough, aes(MN.RecVal_Site,fill=REGION))+ #MN.RecVal_Site #MN.RecVal_Sec #MD.RecVal_Sec_All
  geom_histogram(bins=20)+
  xlim(c(0,.02))+
  facet_grid(Genus_Code~.)
  #facet_grid(~Genus_Code)
sec <- ggplot(ModelParams_SIG_Enough, aes(MN.RecVal_Sec,fill=REGION))+
  geom_histogram(bins=20)+
  xlim(c(0,.02))+
  facet_grid(Genus_Code~.)
secall <- ggplot(ModelParams_SIG_Enough, aes(MD.RecVal_Sec_All,fill=REGION))+ 
  geom_histogram(bins=20)+
  xlim(c(0,.02))+
  facet_grid(Genus_Code~.)
site+sec+secall


```







#Plot full growth model and Genera model
```{r Plotting full growth model 1, }
load("./data/SiteInterval_All_allmodfits_noNAs_Sept14.rdata")

allgrowth <- subset(ColonyLevel, TransitionTypeSimple == "GROWTH" | 
                   TransitionTypeSimple == "SHRINK")
groPOCS <- subset(allgrowth, Genus_Code == "POCS")
groPOSP <- subset(allgrowth, Genus_Code == "POSP")
groMOSP <- subset(allgrowth, Genus_Code == "MOSP")

#avg growth rate for each genus

mean(groPOCS$TransitionRate_L) #cm2/year
mean(groPOSP$TransitionRate_L) #cm2/year
mean(groMOSP$TransitionRate_L) #cm2/year

#Plot full growth model
plot(ln_ESc ~ ln_SS ,data = allgrowth, main="Full growth fit")
abline(a=GrowthDataFrame$g.int[1], b=GrowthDataFrame$g.slp[1], col='red', lwd=2)
legend("topleft", bty = "n", lty = c(1,1), col = c("red"),
       legend= 'All Growth' , cex = 0.8)



#Plot genera model (growth)
png(filename = "figs/GrowthLinRegress.png")
plot(ln_ESc ~ ln_SS ,data = allgrowth, main="Genera growth fit at all sites+ all interval years",
     xlab= "Log10 Starting Size (cm^2)", ylab = "Log10 Ending Size (cm^2)",
     ylim = c(0,8), xlim = c(0,8))
abline(a=data$g.int[1], b=data$g.slp[1], col='red', lwd=2)
abline(a=data$g.int[2], b=data$g.slp[2], col='blue', lwd=2)
abline(a=data$g.int[3], b=data$g.slp[3], col='green', lwd=2)
abline(0, 1, lty=2, col='yellow',lwd=2)
legend("topleft", bty = "n", lty = c(1,1), col = c("red","blue","green","yellow"),
       legend= c(GeneraNames, "1:1 line"), cex = 0.8)
dev.off()

#plot each genus separately
par(mfrow=c(1,3))


#Pocillopora
png(filename = "Figures/GrowthLinReg_POCS.png")
plot(ln_ESc ~ ln_SS ,data = groPOCS,col='black',  
     xlab= "Log10 Starting Size (cm^2)", ylab = "Log10 Ending Size (cm^2)", 
     main="Pocillopora growth fit at all sites+ all interval years",
     ylim = c(0,8), xlim = c(0,8))
abline(a=data$g.int[1], b=data$g.slp[1], lwd=2, col='blue')
abline(0, 1, lty=2,lwd=3,col="gray")
legend("topleft", bty = "n", lty = c(1,1), col = c("blue","gray"),
       legend= c(paste0("y=", round(data$g.slp[1],2),"x+", round(data$g.int[1],3)),"1:1 line"), cex = 0.98)
dev.off()

#Porites
png(filename = "Figures/GrowthLinReg_POSP.png")
plot(ln_ESc ~ ln_SS ,data = groPOSP, col='black',
     xlab= "Log10 Starting Size (cm^2)", ylab = "Log10 Ending Size (cm^2)", 
     main="Porites growth fit at all sites+ all interval years",
    ylim = c(0,8), xlim = c(0,8))
abline(a=data$g.int[2], b=data$g.slp[2], lwd=2, col='yellow')
abline(0, 1, lty=2,lwd=3,col="gray")
legend("topleft", bty = "n", lty = c(1,1), col = c("yellow","gray"),
       legend= c(paste0("y=", round(data$g.slp[2],2),"x+", round(data$g.int[2],3)),"1:1 line"), cex = 0.98)
dev.off()

#Montipora
png(filename = "Figures/GrowthLinReg_MOSP.png")
plot(ln_ESc ~ ln_SS ,data = groMOSP, col='black',
     xlab= "Log10 Starting Size (cm^2)", ylab = "Log10 Ending Size (cm^2)", 
     main="Montipora growth fit at all sites+ all interval years",
     ylim = c(0,8), xlim = c(0,8))
abline(a=data$g.int[3], b=data$g.slp[3], col='green', lwd=2)
abline(0, 1, lty=2,lwd=3,col="gray")
legend("topleft", bty = "n", lty = c(1,1), col = c("green","gray"),
       legend= c(paste0("y=", round(data$g.slp[3],2),"x+", round(data$g.int[3],3)),"1:1 line"), cex = 0.98)
dev.off()
```
#Plotting full growth model 3: Sites
```{r Plotting full growth model3 Sites,}

#Plot full growth model2
LoopLeng <- length(SiteNames)
plot(ln_ESc ~ ln_SS ,data = allgrowth, 
     main="Each site growth fit for all genera + all interval years")
for (i in 1:LoopLeng) {
  abline(a=GrowthDataFrame$g.int[i], b=GrowthDataFrame$g.slp[i], col=i , lwd=2)
}
legend("topleft", bty = "n", lty = c(1,1), col = 1:11,
       legend= SiteNames , cex = 0.8, pt.cex = .7)


#plot each site's growth model separately
par(mfrow=c(4,3))
for (h in 1:LoopLeng) {
  plot(ln_ESc ~ ln_SS ,data = allgrowth, main="Each site growth fit for all genera + all interval years")
    abline(a=GrowthDataFrame$g.int[h], b=GrowthDataFrame$g.slp[h], col=h , lwd=2)
  legend("topleft", bty = "n", lty = c(1,1), col = h,
         legend= SiteNames[h], cex = 0.6, pt.cex = .5)
}

```

#Plot full growth model 4: Interval Years
Each Interval Year for all sites & genera
```{r Plotting full growth model 4,}
#Plot full growth model4
#mad right now bc of NA values
LoopL <- length(IntervalYears)
plot(ln_ESc ~ ln_SS ,data = allgrowth, 
     main="Each interval growth fit for all genera + all sites")
for (m in 1:LoopL) {
  abline(a=GrowthDataFrame$g.int[m], b=GrowthDataFrame$g.slp[m], col=m , lwd=2)
}
legend("topleft", bty = "n", lty = c(1,1), col = 1:11,
       legend= IntervalYears, cex = 0.8, pt.cex = .7)


#which(is.na(Glist_years$g.slp)) #in which index is the glope NA?
#why does interval year 4.26557 have a negative slope?
#ColonyLevel$Site[ColonyLevel$Interval_Years == IntervalYears[10]] #ID the site that is in the 10th position in IntervalYears

#plot each site's growth model separately
par(mfrow=c(4,3))
for (c in 1:LoopL) {
  plot(ln_ESc ~ ln_SS ,data = allgrowth, 
       main="Each interval growth fit for all genera + all sites")
    abline(a=GrowthDataFrame$g.int[c], b=GrowthDataFrame$g.slp[c], col=c , lwd=2)
  legend("topleft", bty = "n", lty = c(1,1), col = c,
         legend= IntervalYears[c], cex = 0.6, pt.cex = .5)
}

```

#Plot full growth model 5: Genera + Site (Work in progress)
Each Interval Year for Sites + Genera
```{r Plotting full growth model 4,}
#loop first for sites. Plot 11 sites
#next loop is from those specific genera at those specific sites


#Plot full growth model5
Loop1 <- length(GeneraNames)
Subloop1 <- length(SiteNames)

plot(ln_ESc ~ ln_SS ,data = allgrowth, 
     main="Each interval year for genera + site")
for (m in 1:Loop1) {
  abline(a=GrowthDataFrame$g.int[m], b=GrowthDataFrame$g.slp[m], col=m , lwd=2)
}
legend("topleft", bty = "n", lty = c(1,1), col = 1:11,
       legend= IntervalYears, cex = 0.8, pt.cex = .7)




#plot each site's growth model separately
par(mfrow=c(4,3))
for (c in 1:LoopL) {
  plot(ln_ESc ~ ln_SS ,data = allgrowth, 
       main="Each interval growth fit for all genera + all sites")
    abline(a=GrowthDataFrame$g.int[c], b=GrowthDataFrame$g.slp[c], col=c , lwd=2)
  legend("topleft", bty = "n", lty = c(1,1), col = c,
         legend= IntervalYears[c], cex = 0.6, pt.cex = .5)
}

```

#Plotting survival models
```{r}
##############
POCS <- ColonyLevel[ColonyLevel$Genus_Code==GeneraNames[3],]
POSP <- ColonyLevel[ColonyLevel$Genus_Code==GeneraNames[2],]
MOSP <- ColonyLevel[ColonyLevel$Genus_Code==GeneraNames[1],]


#plotting logistic regression for presentation
###POCS
surv <- 1 - POCS$Mortality #if it dies it's a 0
POCS$ln_SS <- as.numeric(POCS$ln_SS)
POCS$ln_SS[POCS$ln_SS == -Inf] <-NA
gn_pocs <- glm(surv ~ ln_SS, family = "binomial", data = POCS)
gn_pocs

png(filename = "Figures/SurvivalLogisticRegression_POCS.png")
plot(jitter(surv, 0.1) ~ ln_SS, POCS, 
    xlab= "Log10 Starting Size (cm^2)", ylab = "Survival probability", xlim = c(-1,10),
    main = "Pocillopora Survival: All Sites and Years")
ss <- seq(-3, 9, 0.1)
lines(ss, predict(gn_pocs, list(ln_SS = ss), type="response"), pch=8)
legend("bottomright", bty = "n", col = 1,
       legend= c(paste0("Slope= ", round(gn_pocs$coefficients[2],2)), paste0("Intercept= ", round(gn_pocs$coefficients[1],2)) ))
dev.off()



###POSP
surv <- 1 - POSP$Mortality #if it dies it's a 0
POSP$ln_SS <- as.numeric(POSP$ln_SS)
POSP$ln_SS[POSP$ln_SS == -Inf] <-NA
gn_posp <- glm(surv ~ ln_SS, family = "binomial", data = POSP)
gn_posp

png(filename = "Figures/SurvivalLogisticRegression_POSP.png")
plot(jitter(surv, 0.1) ~ ln_SS, POSP, 
    xlab= "Log10 Starting Size (cm^2)", ylab = "Survival probability", xlim = c(-1,10),
    main = "Porites Survival: All Sites and Years")
ss <- seq(-3, 9, 0.1)
lines(ss, predict(gn_posp, list(ln_SS = ss), type="response"), pch=8)
legend("bottomright", bty = "n", col = 1,
       legend= c(paste0("Slope= ", round(gn_posp$coefficients[2],2)), paste0("Intercept= ", round(gn_posp$coefficients[1],2)) ))
dev.off()


###MOSP
surv <- 1 - MOSP$Mortality #if it dies it's a 0
MOSP$ln_SS <- as.numeric(MOSP$ln_SS)
MOSP$ln_SS[MOSP$ln_SS == -Inf] <-NA
gn_mosp <- glm(surv ~ ln_SS, family = "binomial", data = MOSP)
gn_mosp

png(filename = "Figures/SurvivalLogisticRegression_MOSP.png")
plot(jitter(surv, 0.1) ~ ln_SS, MOSP, 
    xlab= "Log10 Starting Size (cm^2)", ylab = "Survival probability", xlim = c(-1,10),
    main = "Montipora Survival: All Sites and Years")
ss <- seq(-3, 9, 0.1)
lines(ss, predict(gn_mosp, list(ln_SS = ss), type="response"), pch=8)
legend("bottomright", bty = "n", col = 1,
       legend= c(paste0("Slope= ", round(gn_mosp$coefficients[2],2)), paste0("Intercept= ", round(gn_mosp$coefficients[1],2)) ))
dev.off()


```


#Stable size dist for each year
To test assumption that size distribution is stable across time
```{r}
#can't get subset to work....
#ggplot(subset(ColonyLevel, Site%in%c("FFS_OCC_002","FFS_OCC_014"), aes(x=StartingSize, color=Site, fill=Site) )) + xlim(0,5000)+ ylim(0,200) + geom_histogram(bins=15,binwidth=100)+ facet_wrap(~Interval)

sitez <- subset(ColonyLevel, Site=="HAW_SIO_K10")
ggplot(sitez, aes(x=StartingSize, color=Site, fill=Site) ) + xlim(0,5000)+ ylim(0,35) + geom_histogram(bins=15,binwidth=100)+ facet_wrap(~Interval)

#all together
ggplot(ColonyLevel, aes(x=StartingSize, color=Site, fill=Site) ) + xlim(0,5000)+ ylim(0,200) + geom_histogram(bins=15,binwidth=100)+ facet_wrap(~Interval)


```







